The Direction of Search for a Forest Based Bioeconomy

### 2023-09-21 docs/reports/paper/paper1.qmd
update classification description

#### Innovation for a Bioeconomy

@@

# Data and Methods

@@

## Classification Methodology

@@

### Bioeconomy Visions

Innovations were classified as belonging to a bioeconomy vision if they fulfilled one, or more criteria outlined in @bugge2016WhatBioeconomyReview and @vivien2019HijackingBioeconomy.
@tbl-bioeconomy_vision_summary shows the summary of bioeconomy visions presented in the cited papers.
The analysis of bioeconomy discourse which revealed different visions, highlights that the visions have emerged at different times and with different actors at their centers [@vivien2019HijackingBioeconomy, @bugge2016WhatBioeconomyReview].
As discourse elements the bioresource vision developed in

While following these criteria, a number of decisions were made concerning content of the summary presented in @tbl-bioeconomy_vision_summary and the nature of the corresponding vision.
For one, economic growth is cited as the aim & objective of biotechnology and bioresource visions by @bugge2016WhatBioeconomyReview.
It can be argued that all innovation can contribute to economic growth, which is why these aspects were not given heightened importance in the classification decision.
A second topic of judgment has to be the inclusion of innovation which increases the recyclability of a product, or uses recycled waste, water and material in the process.
Based on the definition of a bioecology vision presented in @bugge2016WhatBioeconomyReview, these innovations should be included as contributing to this vision.
The extent to which such innovation contributes in reality to a "[c]ircular and self-sustained production mode" [@bugge2016WhatBioeconomyReview 10], however, can be debated.

:::{#tbl-bioeconomy_vision_summary layout-ncol=1}
+-------------------------------------+------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
|                                     | Biotechnology                                                                      | Bioresource                                                                                                                                                                                                                              | Bioecology                                                                                                                                                                                                                          |
+=====================================+====================================================================================+==========================================================================================================================================================================================================================================+=====================================================================================================================================================================================================================================+
| Aim &   Objectives                  | Economic growth & job   creation                                                   | Economic growth &   sustainability                                                                                                                                                                                                       | Sustainability, biodiversity,   conservation of ecosystems, avoiding soil degradation                                                                                                                                               |
+-------------------------------------+------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Value   Creation                    | Application of biotechnology,   commercialisation of research & technology         | Conversion and upgrading of   bio-resources (process oriented)                                                                                                                                                                           | Development of integrated   production systems and high-quality products with territorial identity                                                                                                                                  |
+-------------------------------------+------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Drivers   & mediators of innovation | R & D, patents, TTOs,   Research councils and funders (Science push, linear model) | Interdisciplinary, optimisation   of land use, include degraded land in the production of biofuels, use and   availability of bio-resources, waste management, engineering, science &   market (Interactive & networked production mode) | Identification of favourable   organic agro-ecological practices, ethics, risk, transdisciplinary   sustainability, ecological interactions, re-use & recycling of waste,   land use, (Circular and self-sustained production mode) |
+-------------------------------------+------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
: Adapted from @bugge2016WhatBioeconomyReview [10] {tbl-colwidths="[25,25,25,25]"}

|  | Type II | Type III | Type I |
|:---|:---|:---|:---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere<br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |
: Adapted from @vivien2019HijackingBioeconomy [194] {tbl-colwidths="[25,25,25,25]"}

Bioeconomy Vision Summary 
:::

@tbl-vision_examples shows five examples of classified innovation.
This selection also highlights that multiple labels can be attached to one innovation.
The last innovation, describing a waterproof paper, is classified as a bioresource vision innovation because it describes a process by which biomass is converted and upgraded.
It is also classified as a biotechnology innovation since the process mimics trees' microfiber formation, according to the innovation source article.

@@

### Eco-Innovation Types

>>>>

## Innovation for a Bioeconomy {#sec-innovation_bioeconomy}

@@

# Data and Methods {#sec-data_methods}

@@

## Classification Methodology {#sec-classification_method}

@@

### Bioeconomy Visions {#sec-bioeconomy_classification_method}

Innovations were classified as belonging to a bioeconomy vision if they fulfilled one, or more criteria outlined in @bugge2016WhatBioeconomyReview and @vivien2019HijackingBioeconomy.
@tbl-bugge and @tbl-vivien show the summary of bioeconomy visions presented in the cited papers.
For the remainder of the paper the nomenclature of @bugge2016WhatBioeconomyReview is adopted.
Vivien et al.'s [-@vivien2019HijackingBioeconomy] Type I bioeconomy is taken to correspond with the bioecology vision, Type II and Type III to correspond with the bioresource and biotechnology vision, respectively.
The analysis of bioeconomy discourse which revealed different visions, highlights that the visions have emerged at different times and with different actors at their centers [@vivien2019HijackingBioeconomy, @bugge2016WhatBioeconomyReview].
@vivien2019HijackingBioeconomy trace the introduction of the term bioeconomics to the 1920s and a work on fishery by the Russian biologist Baranoff.
The term bioeoconomics which they label as Type I bioeconomy, was introduced by Georgescu-Roegen,  in -@roegen1975BioeconomicAspectsEntropy.
@vivien2019HijackingBioeconomy argue that the term biotechnology gradually emerged between 1990 and 2000, in the wake of enthusiasm about biotechnological adavances, such as the discovery of DNA, in preceeding years.
It gained in popularity and international importance when the OECD began increasingly supporting and reshaping its meaning at the turn of the millenium [@vivien2019HijackingBioeconomy].
According to them the last concept to enter the discourse was the bioresource oriented bioeconomy.
While biomass has been used throughout history in various ways, the renewed interest with the intention to replace fossil inputs, for example in European Comission communication since 2010.
However, @vivien2019HijackingBioeconomy point to the long history of biorefinery as a core aspect of this vision, which was discussed as early as the 1930s.
Hence, while the organization of the discourse into the labels biotechnology, bioecology and bioresource vision is a very recent research outcome, the underlying concepts have a richer history.
This alleviates concerns that using these labels retroactively confines the innovations to current policy terms.

While following the criteria of @bugge2016WhatBioeconomyReview and @vivien2019HijackingBioeconomy, a number of decisions were made concerning content of the summary presented in @tbl-bugge and @tbl-vivien, and the nature of the corresponding vision.
For one, economic growth is cited as the aim and objective of biotechnology and bioresource visions by @bugge2016WhatBioeconomyReview.
It can be argued that all innovation can contribute to economic growth, which is why these aspects were not given heightened importance in the classification decision.
A second topic of judgment has to be the inclusion of innovation which increases the recyclability of a product, or uses recycled waste, water and material in the process.
Based on the definition of a bioecology vision presented in @bugge2016WhatBioeconomyReview, these innovations should be included as contributing to this vision.
The extent to which such innovation contributes in reality to a "[c]ircular and self-sustained production mode" [@bugge2016WhatBioeconomyReview 10], however, can be debated.

| | Biotechnology | Bioresource | Bioecology |
|---|---|---|---|
| Aim &   Objectives | Economic growth & job   creation | Economic growth &   sustainability | Sustainability, biodiversity,   conservation of ecosystems, avoiding soil degradation |
| Value   Creation | Application of biotechnology,   commercialisation of research & technology | Conversion and upgrading of   bio-resources (process oriented) | Development of integrated   production systems and high-quality products with territorial identity |
| Drivers   & mediators of innovation | R & D, patents, TTOs,   Research councils and funders (Science push, linear model) | Interdisciplinary, optimisation   of land use, include degraded land in the production of biofuels, use and   availability of bio-resources, waste management, engineering, science &   market (Interactive & networked production mode) | Identification of favourable   organic agro-ecological practices, ethics, risk, transdisciplinary   sustainability, ecological interactions, re-use & recycling of waste,   land use, (Circular and self-sustained production mode) |
: Table adapted from @bugge2016WhatBioeconomyReview [10] {#tbl-bugge}

|  | Type II | Type III | Type I |
|---|---|---|---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere<br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |
: Table adapted from @vivien2019HijackingBioeconomy [194] {#tbl-vivien}

@tbl-vision_examples shows five examples of classified innovation.
This selection also highlights that multiple labels can be attached to one innovation.
The last innovation, describing a waterproof paper, is classified as a bioresource vision innovation because it describes a process by which biomass is converted and upgraded.
It is also classified as a biotechnology innovation since the process mimics trees' microfiber formation, according to the innovation source article.
Lastly, there is also the possibility that an innovation cannot be placed into at least one of the visions.
This is the case for innovation which brings general technological improvements, purely advances economic performance, or relates to a general purpose technology such as appliance of computers.
These innovations are labeled as No Bioeconomy Vision, which does not imply that the innovation is not used, or originates in the forest based bioeconomy as defined above.
An illustrative example of such an innovation are improved work boots, which promote safety of forest workers.

@@

### Eco-Innovation Types {#sec-eco_innovatoin_types}
